### 2023-07-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
blended some plots to get the fig count down

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a
multicomponent vesicle with an initially random distribution of lipids.
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. We first consider the three different
energies---bending, tension, and phase---for each of the
single-component and multicomponent vesicles. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center of mass. As a reminder, the vesicle enters the
constriction at $x=-15$ and exits at $x=15$. Also note that the
single-component vesicle does not have a phase energy. A few general
trends can immediately be seen. First, as the vesicle enters the
stenosis, there are sharp jumps in both the tension and bending
energies, as expected. Next, the multicomponent vesicles only coarsen
when the vesicle is not in the stenosis. Finally, when coarsening does
occur, there are rapid changes in the tension energy.

@@

\begin{figure}[h]
    \centering
    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
    \caption{\label{fig:lubrication} \small The size of the lubrication
    layer of a stiff single-component (red), floppy single-component
    (green), and multicomponent (blue) vesicle passing through stenosis.
    Solid lines are the layer thickness between the vesicle and the top
    wall, and dashed lines are the layer thickness between the vesicle
    and the bottom wall. The reduced area of the vesicles are (a)
    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
\end{figure}

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{(a)}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{(b)}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{(c)}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:tankTreadRAp4} \small The tangential velocity at
  four Lagrangian points on a (a) single-component vesicle with $b = 1$
  (b) single-component vesicle with $b = 0.55$, and (c) multicomponent
  vesicle. The reduced area is $\alpha = 0.4$ in all cases. Also
  illustrated is the vesicle shape and the four Lagrangian points at the
  location indicated by the dash line.}
%\end{figure}
\end{figure*}

@@

\begin{figure}[H]
  \centering
  \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Excess_Pressure_RAp4}
  \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Excess_Pressure_RAp6}
%    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
%    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
  \caption{\label{fig:excessPressure} \small The excess pressure a
  stiff single-component (red), floppy single-component (green), and a
  multicomponent (blue) vesicle moving through stenosis. The reduced
  areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
\end{figure}

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient can be either positive or negative, meaning
that the pressure in the lubrication layer switches signs. This behavior
is caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
=\sigma_s$ which is the usual Marangoni effect.

>>>>

\textcolor{red}{Back of the envelope calculation shows that anything
with reduced area greater than 0.8 can not pass through the stenosis,
assuming the vesicle shape is an ellipse}
We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a
multicomponent vesicle with an initially random distribution of lipids.
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. We first consider the three different
energies---bending, tension, and phase---for each of the
single-component and multicomponent vesicles. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center of mass. As a reminder, the vesicle enters the
constriction at $x=-15$ and exits at $x=15$. Also note that the
single-component vesicle does not have a phase energy. A few general
trends can immediately be seen. First, as the vesicle enters the
stenosis, there are sharp jumps in both the tension and bending
energies, as expected. Next, the multicomponent vesicles only coarsen
when the vesicle is not in the stenosis. Finally, when coarsening does
occur, there are rapid changes in the tension energy.

@@

%\begin{figure}[h]
%    \centering
%    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
%%    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
%%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
%%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
%    \caption{\label{fig:lubrication} \small The size of the lubrication
%    layer of a stiff single-component (red), floppy single-component
%    (green), and multicomponent (blue) vesicle passing through stenosis.
%    Solid lines are the layer thickness between the vesicle and the top
%    wall, and dashed lines are the layer thickness between the vesicle
%    and the bottom wall. The reduced area of the vesicles are (a)
%    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
%\end{figure}

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:tankTreadRAp4} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and tank treading
  velocity of four Lagrangian points of a (a) stiff single-component
  vesicle, (b) floppy single-component vesicle, and (c) multicomponent
  vesicle. The reduced area is $\alpha = 0.4$ in all three cases. Also
  illustrated is the vesicle shape and the four Lagrangian points at the
  location indicated by the dash line. The black dashed line is the
  center line of the channel, and the arrow denotes the tank treading
  direction.}
%\end{figure}
\end{figure*}

@@

%\begin{figure}[H]
%  \centering
%  \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Excess_Pressure_RAp4}
%  \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Excess_Pressure_RAp6}
%%    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
%%    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
%  \caption{\label{fig:excessPressure} \small The excess pressure a
%  stiff single-component (red), floppy single-component (green), and a
%  multicomponent (blue) vesicle moving through stenosis. The reduced
%  areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
%\end{figure}

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient can be either positive or negative, meaning
that the pressure in the lubrication layer switches signs. This behavior
is caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
\sigma_s$ which is the usual Marangoni effect.
